results

### 2020-09-24 analysis/results.Rmd
re-render post
fix pub volume 15-19

```{r}
# required data spreadsheets
# pub volume
els_pub_volume <- readr::read_csv(
  here::here("data", "article_volume_para.csv")
  ) 
# eligble journals 
eligible_jns <- hybrid_df %>% 
  filter(oa_archive == FALSE) %>% 
  distinct(issn)
# pub volume eligble data
hybrid_volume <- els_pub_volume %>%
  filter(issn %in% eligible_jns$issn) %>%
  inner_join(hybrid_df, by = c("issn", "issued_year")) %>%
  filter(oa_archive == FALSE) %>%
  filter(!grepl("^S", page))
# backup 
write_csv(hybrid_volume, here::here("data", "hybrid_volume_eligible.csv"))

@@

# oa
oa_per_jn_year <- hybrid_volume %>%
  group_by(issued_year, issn) %>%
  summarise(oa = n(), .groups = "drop")
oa_ind <- oa_per_jn_year %>%
  group_by(issued_year) %>%
  summarise(oa_n = sum(oa),
            oa_mean = mean(oa),
            oa_sd = sd(oa)) 
# oa uptake 
oa_uptake_ind <- hybrid_volume %>% 
  distinct(issued_year, issn, articles) %>%
  inner_join(oa_per_jn_year, by = c("issn", "issued_year")) %>%
  mutate(prop = oa / articles) %>%
  group_by(issued_year) %>%
  summarise(oa_uptake_mean = mean(prop),
            oa_uptake_sd = sd(prop))
# oa uptake all 
oa_uptake_15_19 <- hybrid_volume %>% 
  distinct(issued_year, issn, articles) %>%
  inner_join(oa_per_jn_year, by = c("issn", "issued_year")) %>%
    group_by(issn) %>%
    summarise(oa = sum(oa),
              articles = sum(articles)) %>%
    mutate(prop = oa / articles)

# all 
total_df <- tibble::tibble(
  issued_year = "2015-19",
  journals = hybrid_volume %>% distinct(issn) %>% nrow(),
  articles_n = hybrid_volume %>% distinct(issn, articles, issued_year) %>% pull(articles) %>% sum(),
  articles_mean = hybrid_volume %>% distinct(issn, articles, issued_year) %>% pull(articles) %>% mean(),
  articles_sd = hybrid_volume %>% distinct(issn, articles, issued_year) %>% pull(articles) %>% sd(),
  oa_n = nrow(hybrid_volume),
  oa_mean = hybrid_volume %>% group_by(issn) %>% summarise(oa = n()) %>% pull(oa) %>% mean(),
  oa_sd = hybrid_volume %>% group_by(issn) %>% summarise(oa = n()) %>% pull(oa) %>% sd(),
  oa_uptake = oa_n / articles_n,
  oa_uptake_mean = mean(oa_uptake_15_19$prop),
  oa_uptake_sd = sd(oa_uptake_15_19$prop)
         )

@@

```{r}
table_descriptives_ind <- tribble(
  ~ind_group, ~ind, ~ind_name,
  "Elsevier Hybrid Journals with OA article(s)", "journals", "Journals",
  "Articles published", "articles_n", "Total",
  "Articles published", "articles_mean", "Avg.",
  "Articles published", "articles_sd", "SD",
  "OA Articles published", "oa_n", "Total OA",
  "OA Articles published", "oa_mean", "Avg.",
  "OA Articles published", "oa_sd", "SD",
  "OA Uptake (in%)", "oa_uptake", "Percentage",
  "OA Uptake (in%)", "oa_uptake_mean", "Avg.",
  "OA Uptake (in%)", "oa_uptake_sd", "SD"
)
inner_join(table_descriptives_ind, ind_summary_table, by = c("ind" = "indicator")) %>%
  dplyr::select(-ind) %>%
  gt(rowname_col = "ind_name", groupname_col = "ind_group") %>%
  fmt_number(contains("20"), decimals = 1) %>%
  fmt_number(contains("20"), 
             rows = c("Total", "Total OA", "Journals"),
             decimals = 0) %>%
  tab_style(
    style = cell_fill(
      color = "grey90"
    ),
    locations = list(
      cells_body(
        columns = "2015-19"
      ),
      cells_column_labels(
        columns = "2015-19"
      )
    )
  ) %>%
  tab_style(
    style = cell_text(color = "black", weight = "bold"),
    locations = list(
      cells_column_labels(everything())
    )
  )  %>%
   tab_style(
    style = cell_text(color = "black", style = "italic"),
    locations = list(
      cells_row_groups())
    ) %>%
  cols_width(
    2 ~ px(125),
    3:7 ~ px(80),
    8 ~ px(110)
  ) %>%
  tab_options(
    row_group.border.top.width = px(3),
    row_group.border.top.color = "white",
    row_group.border.bottom.color = "black",
    table_body.hlines.color = "white",
    table.border.top.color = "white",
    table.border.top.width = px(3),
    table.border.bottom.color = "white",
    table.border.bottom.width = px(3),
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width = px(2),
    stub.border.color = "white"
  )
```

>>>>

```{r}
# required data spreadsheets
# pub volume
els_pub_volume <- readr::read_csv(
  here::here("data", "article_volume_para.csv")
  ) 
# eligble journals 
eligible_jns <- hybrid_df %>% 
  filter(oa_archive == FALSE) %>% 
  distinct(issn)
# pub volume eligible data
hybrid_volume <- els_pub_volume %>%
  filter(issn %in% eligible_jns$issn) %>%
  inner_join(hybrid_df, by = c("issn", "issued_year")) %>%
  filter(oa_archive == FALSE) %>%
  filter(!grepl("^S", page))
# backup 
write_csv(hybrid_volume, here::here("data", "hybrid_volume_eligible.csv"))

@@

# oa
oa_per_jn_year <- hybrid_volume %>%
  group_by(issued_year, issn) %>%
  summarise(oa = n(), .groups = "drop")
oa_ind <- oa_per_jn_year %>%
  group_by(issued_year) %>%
  summarise(oa_n = sum(oa),
            oa_mean = mean(oa),
            oa_sd = sd(oa)) 
# oa uptake 
oa_uptake_ind <- hybrid_volume %>% 
  distinct(issued_year, issn, articles) %>%
  inner_join(oa_per_jn_year, by = c("issn", "issued_year")) %>%
  mutate(prop = oa / articles) %>%
  group_by(issued_year) %>%
  summarise(oa_uptake_mean = mean(prop),
            oa_uptake_sd = sd(prop))
# oa uptake all 
oa_uptake_15_19 <- hybrid_volume %>% 
  distinct(issued_year, issn, articles) %>%
  inner_join(oa_per_jn_year, by = c("issn", "issued_year")) %>%
    group_by(issn) %>%
    summarise(oa = sum(oa),
              articles = sum(articles)) %>%
    mutate(prop = oa / articles) 
# article volume 2015-19
volume_15_19 <- els_pub_volume %>%
  # elgible journals
  filter(issn %in% eligible_jns$issn) %>%
  summarise(n = sum(articles),
            mean_articles = mean(articles),
            sd = sd(articles))

# all 
total_df <- tibble::tibble(
  issued_year = "2015-19",
  journals = hybrid_volume %>% distinct(issn) %>% nrow(),
  articles_n = volume_15_19$n,
  articles_mean = volume_15_19$mean_articles,
  articles_sd = volume_15_19$sd,
  oa_n = nrow(hybrid_volume),
  oa_mean = hybrid_volume %>% group_by(issn) %>% summarise(oa = n()) %>% pull(oa) %>% mean(),
  oa_sd = hybrid_volume %>% group_by(issn) %>% summarise(oa = n()) %>% pull(oa) %>% sd(),
  oa_uptake = oa_n / articles_n,
  oa_uptake_mean = mean(oa_uptake_15_19$prop),
  oa_uptake_sd = sd(oa_uptake_15_19$prop)
         )

@@

```{r}
table_descriptives_ind <- tribble(
  ~ind_group, ~ind, ~ind_name,
  "Elsevier Hybrid Journals with OA article(s)", "journals", "Journals",
  "Articles published", "articles_n", "Total",
  "Articles published", "articles_mean", "Avg.",
  "Articles published", "articles_sd", "SD",
  "OA Articles published", "oa_n", "Total OA",
  "OA Articles published", "oa_mean", "Avg.",
  "OA Articles published", "oa_sd", "SD",
  "OA Uptake (in%)", "oa_uptake", "Percentage",
  "OA Uptake (in%)", "oa_uptake_mean", "Avg.",
  "OA Uptake (in%)", "oa_uptake_sd", "SD"
)
gt_1 <- inner_join(table_descriptives_ind, ind_summary_table, by = c("ind" = "indicator")) %>%
  dplyr::select(-ind) %>%
  gt(rowname_col = "ind_name", groupname_col = "ind_group") %>%
  fmt_number(contains("20"), decimals = 1) %>%
  fmt_number(contains("20"), 
             rows = c("Total", "Total OA", "Journals"),
             decimals = 0) %>%
  tab_style(
    style = cell_fill(
      color = "grey90"
    ),
    locations = list(
      cells_body(
        columns = "2015-19"
      ),
      cells_column_labels(
        columns = "2015-19"
      )
    )
  ) %>%
  tab_style(
    style = cell_text(color = "black", weight = "bold"),
    locations = list(
      cells_column_labels(everything())
    )
  )  %>%
   tab_style(
    style = cell_text(color = "black", style = "italic"),
    locations = list(
      cells_row_groups())
    ) %>%
  cols_width(
    2 ~ px(125),
    3:7 ~ px(80),
    8 ~ px(110)
  ) %>%
  tab_options(
    row_group.border.top.width = px(3),
    row_group.border.top.color = "white",
    row_group.border.bottom.color = "black",
    table_body.hlines.color = "white",
    table.border.top.color = "white",
    table.border.top.width = px(3),
    table.border.bottom.color = "white",
    table.border.bottom.width = px(3),
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width = px(2),
    stub.border.color = "white"
  )
gt_1
#gt::gtsave(gt_1, here::here("figure", "gt_overview.png"), dpi = 300)
```
